Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model

### 2022-01-18 response1_BMB.tex
reviewer 1 covered

\res 2
Regarding the incorporation of an exposed class or asymptomatic and infectious compartment to the current model; I think

@@

* Due to its important effects on R0, I think it could be useful to describe the rate $\omega$ for return of test results directly in the text (in addition to the table of parameters) before it appears in Equation 4 in the expression for the disease-free equilibrium.

* In Section A.4 of the appendix, is the partial derivative of $\Delta$ being calculating for the exact expression from Equation 7, or from the approximate expression in Equation A22 obtained from a Taylor expansion when $\rho \ll 1$. From the expression in Equation A27, it seems like this is derived from Equation 7, but it would be helpful to clarifying which expression is used to highlight whether this result holds across the range of parameters or only in the limit of weak testing intensity.

>>>>

\res 2
[not sure here!] 
Regarding the incorporation of an exposed class or asymptomatic and infectious compartment to the current model; the isolation efficacy parameter $\theta_X$ would have similar but stronger effects (result 1).

@@

\com 3 
Due to its important effects on R0, I think it could be useful to describe the rate $\omega$ for return of test results directly in the text (in addition to the table of parameters) before it appears in Equation 4 in the expression for the disease-free equilibrium.

\res 3
We now have added a line in the manuscript to describe the parameters involved in the DFE before Equation (4)

\com 4
In Section A.4 of the appendix, is the partial derivative of $\Delta$ being calculating for the exact expression from Equation 7, or from the approximate expression in Equation A22 obtained from a Taylor expansion when $\rho \ll 1$. From the expression in Equation A27, it seems like this is derived from Equation 7, but it would be helpful to clarifying which expression is used to highlight whether this result holds across the range of parameters or only in the limit of weak testing intensity.

\res 4
We have added a line in the manuscript in Section A.4 of the appendix to clarify the fact that Eq. 27 is a direct result of differentiating $\Delta$ in Eq.7 with respect to $w_{IS}$.
